---
title: "R_tutorial_1"
author: "Edu Lastra Cancela"
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
---
## Q1. Assigning values

Create an object called `height` with the value 175 and print it.

```{r q1}
height <- 175
print(height)
``` 
## Q2. Simple math

##Calculate the result of 25 * 4 - 10.

```{r q2}
25 * 4 - 10
```
## Q3. Using functions

Use `sqrt()` to calculate the square root of 81.

```{r q3}
sqrt(81)
```
## Q4. Character objects

Assign the phrase "R is fun!" to an object called `message` and print it.

```{r q4}
message <- "R is fun!"
print(message)
```
## Q5. Object manipulation

Create `a` and `b`, calculate their sum, and store it in `c`.

```{r q5}
a <- 10
b <- 5
c <- a + b
print(c)
```
## Q6. Logical comparison

Test whether 15 is greater than 20.

```{r q6}
15 > 20
```
## Q7. Checking classes

Check the class of `"Hello World"`.

```{r q7}
class("Hello World")
```
## Q8. Suppressing warnings

### Before: warnings displayed

The original code runs with `warning = TRUE`.

```{r q8-before, warning=TRUE}
log(-1)
```
### After: warnings suppressed

Only the chunk option changes to `warning = FALSE`; the code stays the same.

```{r q8-after, warning=FALSE}
log(-1)
```
## Q9. Suppressing messages

```{r q9-prepare, include=FALSE}
# Make the first example reproducible if dplyr is already attached.
if ("package:dplyr" %in% search()) {
  detach("package:dplyr", character.only = TRUE)
}
```
### After: messages suppressed

Only the chunk option changes to `message = FALSE`; the code stays the same.

```{r q9-after, message=FALSE}
# Load a package (may produce messages)
library(dplyr)
```

## Q10. Creating and analyzing a vector

Create the numeric vector `grades`, calculate its mean, store the result
in `average`, and print it.

```{r q10}
grades <- c(80, 90, 75, 95, 85)
average <- mean(grades)
print(average)
```